Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix

### 2018-03-09 r1doc/RebuttalTetrahelixUntwistV2.tex

The equitetrabeam is introduced as a special case that the rail angle is zero. It is proposed that
transformation from tetrahelix to equitetrabeam is possible by changing the minimax ratio about
16\%.

Overall, this paper is acceptable, but requires some revision. The following includes some comments.

\subsection{Modification}
\begin{itemize}
\item
The sentences of this paper need to be compact. Please read several times and then clean
the sentences.
``without loss of generality'' $\rightarrow$ ``generally''
\highlighttext{The term ``without loss of generality'' is being used specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowed in a proof because of symmetry or an ability to make
  a choice that does not change the validity of the proof.
  However, because this was unclear to the reviewer, in order to clarify this, I have added the word ``assume'' to the first use of the phrase ``without loss of generality'' and the phrase ``By symmetry'' to the second use.
  }

\item
  The explanation for figure 8 can be erased by drawing the general case for figure 8.
  \highlighttext{Yes, you are correct, thank you, I have made the diagram (see \cref{fig:wobble}) more general and removed the
    disclaiming text.}
    \begin{figure}
     \centering
     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram2.png}
     \caption{Wobble Vectors from Non-Coincident Axes}
  \label{fig:wobble}
\end{figure}
  \item
    Instead of sentence starting to ‘we……’ , the passive sentence is recommended.
    \highlighttext{
      I believe editorial opinion is somewhat divided\cite{firstperson} on the use of the word ``we'' when it is used to mean ``the author and the reader together'' as I have used it. Most editors do not prefer passive sentences in general.
      Nonetheless, in deference to the reviewer, I have searched the paper for each use of the ``we'' and
      removed it in most, but not all cases.
      }
    \item 
 The following sentence is obscure. You'd better suggest a way to measure optimality using
 some kinematic indices :
\begin{quote}
 We have not yet proved that a two-class tetrahelix is optimal, but it suffices to show
that there exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
\end{quote}

@@

\highlighttext{
  The reviewer has generally noted that I may not have motivated my definition of ``optimality''
  strongly enough. To improve this, I have made some changes:
... displays a continuum of tetrahelices optimal in a \bf{
  in the sense of being
as regular as possible},
which is the main result of this
paper.
}

\highlighttext{
  Additionally, in the section on Optimal Tetrahelices, I have inserted the following sentence which helps to
  explain the definition of optimality:
  \bf{By maintaining all lengths as close to the same ``regular'' length as possible,
such as the mean length of the actuator,
one retains the greatest possible freedom of motion for the robot.}
  }

\highlighttext{This specific sentence has been clarified to show that ``not yet proved'' means
  ``not yet reached the proof in this paper of that fact that'' by changing the sentence to refer
  to the next theorem:
  \begin{quote}
  We have not yet {\em
proved theorem 3 which asserts} that a two-class tetrahelix is optimal, but it suffices to show that there
exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
  \end{quote}
  I unfortunately am not sure how to relate this notion of optimality to kinematic indexes, but
  have attempted elsewhere to clarify why this definition of optimality is valuable for
  Tetrobot-style robots.
  }
\item 
 It is recommended to change:
 ``conincident'' $\rightarrow$ ``coincident''
 \highlighttext{Corrected--an embarassing mistake in my spelling correction software.}
 \item
\item In page 3, after the eq. (4)
  In this formula, ``integral values of n'' $\rightarrow$ In this formula, ``integer values of n''
  \highlighttext{Corrected.}
  \item 
In eq. (23), need to be changed as

\begin{equation}
  \begin{split}
  \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ j_{\rho})}}
       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+k_{\rho}) }} \text{.}
  \end{split}       
\end{equation}
$\rightarrow$ 
\begin{equation}
  \begin{split}
  \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ k_{\rho})}}
       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+j_{\rho}) }} \text{.}
  \end{split}       
\end{equation}
\highlighttext{This has been corrected, thanks for the careful catch of an embarrassing mistake.}

### 2018-03-09 r1doc/RebuttalTetrahelixUntwistV2.tex

\date{\today}
% Hint: \title{what ever}, \author{who care} and \date{when ever} could stand 
% before or after the \begin{document} command 
% BUT the \maketitle command MUST come AFTER the \begin{document} command! 
\begin{document}

\maketitle

\section{Thanks}

The author wishes to thank the reviewers for their careful and attentive work, that has
significantly improved the paper. Each comment is responded
to below, on a point-by-point basis.

@@

\subsection{Modification}
\begin{itemize}
\item
The sentences of this paper need to be compact. Please read several times and then clean
the sentences.
``without loss of generality'' $\rightarrow$ ``generally''
\highlighttext{The term ``without loss of generality'' is being used specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowed in a proof because of symmetry or an ability to make
  a choice that does not change the validity of the proof.
  However, because this was unclear to the reviewer, in order to clarify this, I have added the word ``assume'' to the first use of the phrase ``without loss of generality'' and the phrase ``By symmetry'' to the second use.
  }

\item
  The explanation for figure 8 can be erased by drawing the general case for figure 8.
  \highlighttext{Yes, you are correct, thank you, I have made the diagram (see \cref{fig:wobble}) more general and removed the
    disclaiming text.}
    \begin{figure}
     \centering
     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram2.png}
     \caption{Wobble Vectors from Non-Coincident Axes}
  \label{fig:wobble}
\end{figure}
  \item
    Instead of sentence starting to ‘we……’ , the passive sentence is recommended.
    \highlighttext{
      I believe editorial opinion is somewhat divided\cite{firstperson} on the use of the word ``we'' when it is used to mean ``the author and the reader together'' as I have used it. Most editors do not prefer passive sentences in general.
      Nonetheless, in deference to the reviewer, I have searched the paper for each use of the ``we'' and
      removed it in most, but not all cases.
      }
    \item 
 The following sentence is obscure. You'd better suggest a way to measure optimality using
 some kinematic indices :
\begin{quote}
 We have not yet proved that a two-class tetrahelix is optimal, but it suffices to show
that there exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
\end{quote}

\highlighttext{
  The reviewer has generally noted that I may not have motivated my definition of ``optimality''
  strongly enough. To improve this, I have made some changes:
... displays a continuum of tetrahelices optimal \bf{
  in the sense of being
as regular as possible},
which is the main result of this
paper.
}

@@

\highlighttext{
  Additionally, in the section on Optimal Tetrahelices, I have inserted the following sentence which helps to
  explain the definition of optimality:
  \bf{By maintaining all lengths as close to the same ``regular'' length as possible,
such as the mean length of the actuator,
one retains the greatest possible freedom of motion for the robot.}
  }

\highlighttext{This specific sentence has been clarified to show that ``not yet proved'' means
  ``not yet reached the proof in this paper of that fact that'' by changing the sentence to refer
  to the next theorem:
  \begin{quote}
  We have not yet {\em
proved theorem 3 which asserts} that a two-class tetrahelix is optimal, but it suffices to show that there
exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
  \end{quote}
  I unfortunately am not sure how to relate this notion of optimality to kinematic indexes, but
  have attempted elsewhere to clarify why this definition of optimality is valuable for
  Tetrobot-style robots.
  }
\item 
 It is recommended to change:
 ``conincident'' $\rightarrow$ ``coincident''
 \highlighttext{Corrected--an embarrassing mistake in my spelling correction software.}
 \item
\item In page 3, after the eq. (4)
  In this formula, ``integral values of n'' $\rightarrow$ In this formula, ``integer values of n''
  \highlighttext{Corrected.}
  \item 
In eq. (23), need to be changed as

@@

This paper proposed a method to transform the BC helix to Planar-faced tetrahelix by minimizing the difference between the longest and shortest edges, under some constraints. The author tried to explain his finding logically, and the background of the research is explained well. Also, the author shared the materials for this research at github. I have some comments for this paper as follows:

\begin{enumerate}

  \item
 I can see the organization of this paper is as follows: 
 Intro (2pages) – A designer’s formulation for the BC helix(2 pages) – Optimal tetrahelices are triple helix(3 pages) – Parameterizing tetrahelices via rail angle(2 pages) – The inradius(0.5 pages) – The Equitetrabeam (0.5 pages) – An Untwisted continuum (0.5 pages) – Conclusion
 \item 
   I think the author tried to explain all the findings but I think the organization of the paper should be revised to be emphasized carefully. Even for the researchers in this field, I am not convinced the paper is clearly written to emphasize the contribution well. Some sections can be combined, and the organization should be changed to emphasize the major contribution of this paper. I think this is the most significant point to improve the readability of the paper.

   \highlighttext {
The remainder of this  paper:
\begin{enumerate}
\item provides a new formulation for the BC helix that is more natural for engineers,
\item defines a concept of minimum maximum edge-length optimality that maintains
  the structure as close to regularity as possible,
  \item proves that all
    optimal tetrahelices are in fact triple helices,
\item provides formulae for constructing optimal tetrahelices of different twists or for optimally
    transforming a
    robot from a twisted to a planar configuration in a way that maintains optimum regularity,
\item gives a formula for the inradius of an optimal tetrahelix,
\item describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
  a structural beam or for applying standard robot gaits to a tetrahedral robot, and
\item discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
  \end{enumearate}
}

@@

  \item
    I think the explaining optimization part should be revised. For a certain optimization problem, I think mathematics definition or algorithmic explanation can be helpful to understand the problem quickly. I think the author should refer problem definition standards from other optimization papers to revise this.
    \highlighttext{
      In order to clarify the ``Optimal Tetrahelices are Triple Helices'' section as requested,
      I have provided a mathematical description of the optimization, and a more mathematical
      description of the definition of the tetrahelix.
      }

  \item    
    In my opinion, the problem definition and proof of theorems looks being done based on personal experiences. I recommend using mathematical derivation or expression if possible.
    \highlighttext{
      I believe the theorems are all true (and verified by computer experimentation) and that the proofs
      are rigorous. However, in deference to the reviewer I have significantly rewritten parts of them
      more formally in several places. Unfortunately, it is beyond my ability to make them completely formal
      in the space allowed in this paper. I hope readers will find them convincing at the available length.
      }

  \item    
    I think the demonstration by experiment can be helpful to understand the idea. Video attachment is recommended.
    \highlighttext{
I have included a public link to a video\cite{tetrahelixvideo} in the citations, and will upload the same video to the journal if appropriate.
\begin{quote}All math
developed here is available in JavaScript and demonstrated by an interactive
design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
\bf{and a video\cite{tetrahelixvideo}},
from which figs. 1 and 2 and later figures in this paper 
are taken.      
\end{quote}
    }

### 2018-03-09 r1doc/TetrahelixUntwistV2.tex
yet another update

\Cref{fig:series} displays a continuum of tetrahelices optimal in a \highlighttext{in the sense of being
as regular as possible},
which is the main result of this
paper. The closest helix is the BC helix, and the furthest
is the equitetrabeam, defined in \cref{sec:equitetrabeam} and \cref{fig:naming,fig:equitetrabeam}.

@@

\highlighttext{
The remainder of this  paper:
\begin{enumerate}
\item Provides a new formulation for the BC helix that is more natural for engineers,
\item Defines a concept of minimum maximum edge-length optimality and proves that all
    optimal tetrahelices are in fact triple helices,
\item Provides formulae for constructing optimal tetrahelices of different twists or for optimally
    transforming a
    robot from a twisted to a planar configuration,
\item Gives a formula for the inradius of an optimal tetrahelix,
\item Describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
  a structural beam or for applying standard robot gaits to a tetrahedral robot, and
\item Discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
\end{enumerate}
}

@@

Now that \highlighttext{it is provent that the} axes are coincident and parallel and that the pitches
are the same for all helices, any optimum tetrahelix can
be generated with a \highlighttext{simple} equation for helices:
\begin{equation}
\label{eq:triple}
\vec{V}_{triple}(n,c) =
\left [
  \begin{tabular}{c}
   $ r_c \cos(n \alpha +  c 2 \pi /3 + \phi_c)$\\
   $ r_c \sin(n \alpha +  c 2 \pi /3 + \phi_c) $\\
   $ \frac{d(n +c / 3)}{3}   $
  \end{tabular}
  \right ],
\end{equation}
\text{where: \qquad}
\begin{tabular}{l}
  $c \in \{0,1,2\}$,
  \end{tabular}      
which would be much more complicated if the axes where not coincident.
\highlighttext{
Having not yet investigated in the general case the relationships beteween
$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple} for the three helices
(the relationships are developed in \cref{eqrhoopt}) these are denoted with a $c$ subscript to show
they are dependent on the color ($c \in \{R,B,Y\}$).
Since any optimal tetrahelix is described by \cref{eq:triple},
\[
rad(\vec{V}_{triple}(n,c)) = max \{r_R, r_B, r_Y\}
\]
}

\highlighttext{This equation does not completely explain} the  relationships beteween
$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple}.
In \cref{sec:parameterizing}, we give a more specific version of this formula which
generates optimal tetrahelices.
\highlighttext{Observe} that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
but because of the $\phi_c$ term, they are not collinear.

>>>>

\Cref{fig:series} displays a continuum of tetrahelices optimal \highlighttext{in the sense of being
as regular as possible},
which is the main result of this
paper. The closest helix is the BC helix, and the furthest
is the equitetrabeam, defined in \cref{sec:equitetrabeam} and \cref{fig:naming,fig:equitetrabeam}.

@@

\highlighttext{
The remainder of this  paper:
\begin{enumerate}
\item provides a new formulation for the BC helix that is more natural for engineers,
\item defines a concept of minimum maximum edge-length optimality that maintains
  the structure as close to regularity as possible,
  \item proves that all
    optimal tetrahelices are in fact triple helices,
\item provides formulae for constructing optimal tetrahelices of different twists or for optimally
    transforming a
    robot from a twisted to a planar configuration in a way that maintains optimum regularity,
\item gives a formula for the inradius of an optimal tetrahelix,
\item describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
  a structural beam or for applying standard robot gaits to a tetrahedral robot, and
\item discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
\end{enumerate}
}

@@

Now that \highlighttext{it is proven that the} axes are coincident and parallel and that the pitches
are the same for all helices, any optimum tetrahelix can
be generated with a \highlighttext{simple} equation for helices:
\begin{equation}
\label{eq:triple}
\vec{V}_{triple}(n,c) =
\left [
  \begin{tabular}{c}
   $ r_c \cos(n \alpha +  c 2 \pi /3 + \phi_c)$\\
   $ r_c \sin(n \alpha +  c 2 \pi /3 + \phi_c) $\\
   $ \frac{d(n +c / 3)}{3}   $
  \end{tabular}
  \right ],
\end{equation}
\text{where: \qquad}
\begin{tabular}{l}
  $c \in \{0,1,2\}$,
  \end{tabular}      
which would be much more complicated if the axes where not coincident.
\highlighttext{
Having not yet investigated in the general case the relationships beteween
$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple} for the three helices
 these are denoted with a $c$ subscript to show
they are dependent on the color ($c \in \{R,B,Y\}$).
In \cref{sec:parameterizing}, we give a more specific version (\cref{eqrhoopt}) of this formula which
generates optimal tetrahelices.
Since any optimal tetrahelix is described by \cref{eq:triple},
\[
rad(\vec{V}_{triple}(n,c)) = max \{r_R, r_B, r_Y\}
\]
}

\highlighttext{Observe} that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
but because of the $\phi_c$ term, they are not collinear.
